Thermodynamic response functions in a cell fluid model

### 2024-09-03 main_morse_response_functions.tex
add appendix for explicit expressions of derivatives

	The quantity $\tilde D(0)$ entering equations~\eqref{eq:eosMT} and~\eqref{chem_pot} is a function of temperature
	\begin{equation}
	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
	\end{equation}
	The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite[see Eq.(31)]{KozlovskiiDobush2020}
	\begin{equation}
		k_{\rm B}T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
	\end{equation}

@@

	\newpage

@@

>>>>

	The quantity $\tilde D(0)$ entering equations~\eqref{eq:eosMT} and~\eqref{chem_pot} is a function of temperature
	\begin{equation}
	\label{def:D0}
	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)}.
	\end{equation}
	The condition $\tilde{D}(0) = 0$ defines the critical temperature~\cite[see Eq.(31)]{KozlovskiiDobush2020}
	\begin{equation}
		k_{\rm B}T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
	\end{equation}

@@

	%\newpage

@@

	\appendix
	\renewcommand{\theequation}{A.\arabic{equation}}
	\setcounter{equation}{0}

	\section{\label{sec:app-a} Explicit expressions for derivatives}
	In this appendinx, explicit expressions are presented for derivatives of quantities entering the equation of state, with respect to temperature. This expressions are useful while calculating the response functions in Section~\ref{sec:respons_functions}.

	For the quantity $\bar{M}$ from Eq.~\eqref{eq:M_nT} one has
	\begin{equation}
		\left( \frac{\partial \bar{M}}{\partial \tau} \right)_{\bar{n}} =
		\frac{k_{\rm B}T_c \rho_n}{W(0)} \frac{1 - \omega_0}{1 + \tau\omega_0},
	\end{equation}
	where
	\begin{equation*}
		\omega_0 = \frac{\chi_0 + A_{\gamma}}{B - 1 + \chi_0}.
	\end{equation*}
	For $\tilde{D}(0)$ from~\eqref{def:D0} one has
	\begin{equation}
		\frac{\partial \tilde{D}(0)}{\partial \tau} = -\frac{k_{\rm B}T_c}{W(0)} \frac{1 - \omega_0}{1 + \tau \omega_0}.
	\end{equation}
